Cluster Difference Imaging Photometric Survey (CDIPS) II. TOI~837: A Young Validated Planet in IC~2602

### 2020-07-31 paper/ms.tex
update manuscript

If the RM measurements prove that the validated planet is real, a
campaign to measure the mass timed to coincide with TESS sectors 36
and 37 (late March to late May of 2021) would significantly ease the
extraction of the planetary mass.  The reason is that the RVs,
activity indicators, and photometry could be modeled simultaneously
\citep[{\it e.g.},][]{rajpaul_gaussian_2015}. This would greatly
constrain models of the spot-induced RV signal.  The mass measurement
would be a worthy goal in order to improve understanding of the
planet's contraction and photoevaporation history.

>>>>

If the RM measurements prove that the validated planet is real,
measuring its mass may be worth the effort, because it would improve
understanding of the planet's contraction and photoevaporation.  If an
RV campaign were timed to coincide with TESS sectors 36 and 37 (3
March 2021 through 28 April 2021), it would significantly ease
extraction of the Keplerian signal.  The reason is that the RVs,
activity indicators, and photometry could be modeled simultaneously
\citep[{\it e.g.},][]{aigrain_simple_2012,rajpaul_gaussian_2015}.
Combining photometric and radial velocity data from non-overlapping
epochs would also constrain the models, but perhaps not quite as
convincingly.
